%-------------------------
% CV in LaTeX
% Author : Gustavo Acosta
%------------------------

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{newtxtext}
\usepackage[margin=0.5in,top=0.47in,bottom=0.55in]{geometry}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=*, itemsep=0pt, topsep=0.5pt, parsep=0pt, partopsep=0pt}
\linespread{1.0}

% Sections formatting
\titleformat{\section}{
  \vspace{-1pt}\scshape\raggedright\normalsize
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]
\titlespacing*{\section}{0pt}{5pt}{3pt}

% Custom commands
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeItem}[1]{
  \item {\small #1}
}

\newcommand{\resumeSubItem}[1]{
  \item {\small #1}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gustavoacostam.github.io/}{\Large Gustavo Acosta}}
  & \href{mailto:gustavoa@umich.edu}{gustavoa@umich.edu} \\
  \href{https://github.com/gustavoacostam/}{GitHub}
  &
\end{tabular*}

%-----------FIELDS-----------
\section{Fields of Interest}
Development Economics, Global Health Economics, Labor Economics

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Michigan}{}{Ph.D. Candidate in Economics}{2023--Present}
  \resumeSubheading
    {University of Michigan}{}{M.A. in Economics (Pathway to Ph.D.)}{2025}
  \resumeSubheading
    {Pontifical Catholic University of Peru (PUCP)}{}{B.Sc. in Economics}{2013--2018}
\resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {University of Michigan}{}{Research Associate}{2024--2025}
    \begin{itemize}
      \resumeItem{PI: Emma Riley. Project on adolescent girls' economic and social empowerment in Tanzania (2025).}
      \resumeItem{PI: Elisa Maffioli. Projects on malaria vaccines and fake drugs in Africa (2024--2025).}
    \end{itemize}

  \resumeSubheading
    {Duke University}{}{Pre-Doctoral Research Fellow}{2020--2023}
    \begin{itemize}
      \resumeItem{PIs: Erica Field, Robert Garlick, and Katherine Vyborny. Projects in Peru and Pakistan on health, gender, labor markets, and survey methodology.}
    \end{itemize}

  \resumeSubheading
    {Innovations for Poverty Action}{}{Senior Research Associate}{2018--2020}
    \begin{itemize}
      \resumeItem{Peru. PIs: Erica Field, Livia Schubiger, and Javier Romero. Projects on health and gender-based violence.}
      \resumeItem{Paraguay. PI: Nathan Fiala. Projects on poverty and financial inclusion.}
    \end{itemize}

\resumeSubHeadingListEnd

%-----------WORKING PAPERS-----------
\section{Working Papers}
\resumeSubHeadingListStart

  \resumeSubItem{Are Insiders or Community Leaders Effective in Identifying Intimate Partner Violence? With Erica Field. Draft available upon request.}
  \resumeSubItem{Text Messaging for Mental Health Management During the COVID-19 Pandemic. With Erica Field, Daniel Hurtado, and Javier Romero. Draft available upon request.}
  \resumeSubItem{Imprecise Beliefs About Malaria Infection Risk and Vaccine Protection in Ghana (Third-Year Paper). Draft available upon request.}
  \resumeSubItem{Higher Education Reforms and Political Outcomes. With Leah Lakdawala and Fabiola Alba. Draft available upon request.}

\resumeSubHeadingListEnd

%-----------WORK IN PROGRESS-----------
\section{Work in Progress}

\resumeSubHeadingListStart
  \resumeSubItem{Enhancing Women's Safety in Public Spaces: Training Community Volunteers to Reduce Gender-Based Violence in Peru. With Marcia Ruiz and Guiliana Campos. Pilot completed, with data collection scheduled for 2026.}
  \resumeSubItem{Sustaining Public Infrastructure: A Gender-Informed Behavioral Intervention for Housing Maintenance in Peru. With Marcia Ruiz and Emily Saavedra. Baseline completed, with data collection scheduled for 2026.}
  \resumeSubItem{Targeting Men to Reduce Domestic Violence: An Evaluation of Men for Equality. With Erica Field. Baseline completed, with endline data collection scheduled for 2026.}
  \resumeSubItem{Sustaining Shared Urban Sanitation in Uganda. With Marcia Ruiz and Laston Manja. Pilot completed, with data collection scheduled for 2026.}
  \resumeSubItem{The Price of Safety: The Effects of Extortion on Small-Scale Entrepreneurship in Peru. With Gabby Lecaro. Data collection scheduled for 2026.}
  \resumeSubItem{Formal Savings Adoption Among Vulnerable Populations in Colombia: Evidence from a Banca de las Oportunidades Intervention. With Tommaso Crosta. Implementation funding secured, with fieldwork preparation underway for 2026.}
  \resumeSubItem{Providing Real-Time, Accurate Data to Increase Malaria Vaccine Completion Rates in Ghana. With Jessica Cohen and Elisa Maffioli. Baseline completed.}
  \resumeSubItem{Mitigating the Impact of Health and Climate Shocks on School Performance in Malawi: The Role of School Management Structures. With Laston Manja.}
  \resumeSubItem{Evaluating OCP Nigeria's Farm \& Fortune Hubs and OCP School Lab. With Nilesh Fernando. Design stage.}
  \resumeSubItem{School Feeding and Human Capital Development in Peru. With Muchin Bazan and Shahadath Hossain.}
\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Pre-Doctoral Publications}
\resumeSubHeadingListStart
  \resumeSubItem{Acosta, G. and P. Francke. 2021. \href{http://revistas.up.edu.pe/index.php/apuntes/article/view/1228/1525}{``Impact of the Qali Warma School Feeding Program on Chronic Child Malnutrition.''} \textit{Apuntes}.}
  \resumeSubItem{Acosta, G. and P. Francke. 2020. \href{http://www.scielo.org.pe/pdf/rmh/v31n3/1729-214X-rmh-31-03-148.pdf}{``Impact of Micronutrients `Sprinkles' on Chronic Childhood Malnutrition in Peru.''} \textit{Revista M\'edica Herediana}.}
\resumeSubHeadingListEnd

%-----------POLICY NOTES-----------
\section{Policy Notes}
\resumeSubHeadingListStart
  \resumeSubItem{Acosta, G., E. Field, H. Khan, and K. Vyborny. 2023. \textit{Lockdowns and Learning Outcomes: Insights from 10th Grade Examination Results in Pakistan}. C-19 Notes, PEDL.}
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards, Fellowships, and Grants}
\resumeSubHeadingListStart
  \resumeSubItem{Peruvian Government Funding through IPA Peru, \textit{Targeting Men to Reduce Domestic Violence: An Evaluation of Men for Equality}. Co-PI with Erica Field --- USD \$90,000 (2026).}
  \resumeSubItem{Marshall Weinberg Population, Development and Climate Change Fellowship, Institute for Social Research, University of Michigan, \textit{Sustaining Shared Urban Sanitation in Uganda}. Lead-PI with Marcia Ruiz and Laston Manja --- USD \$8,500 (2026).}
  \resumeSubItem{J-PAL Crime and Violence Initiative (CVI), Pre-Approval, \textit{Sexual Harassment in Peru}. Lead-PI with Marcia Ruiz --- USD \$50,000 (2026).}
  \resumeSubItem{Sexual Violence Research Initiative (SVRI), \textit{Sexual Harassment in Peru}. Lead-PI with Marcia Ruiz and Pedro Francke --- USD \$100,000 (2026).}

  \resumeSubItem{The Weiss Fund, \textit{Sexual Harassment in Peru}. --- USD \$25,000 (2025).}
  \resumeSubItem{University of Michigan PACLSHR, \textit{Sexual Harassment in Peru}. --- USD \$6,000 (2025).}
  \resumeSubItem{Rackham Graduate Student Research Grant, \textit{Sexual Harassment in Peru}. --- USD \$1,500 (2025).}
  \resumeSubItem{Rackham Graduate Student Research Grant, \textit{Extortion in Peru}. Co-PI with Gabby Lecaro --- USD \$1,500 (2025).}

  \resumeSubItem{Sylff Research Grant, \textit{Sustaining Public Infrastructure in Peru}. Lead-PI with Marcia Ruiz --- USD \$10,000 (2025).}
  \resumeSubItem{Rackham Graduate Student Research Grant, \textit{Sustaining Public Infrastructure in Peru}. Co-PI with Marcia Ruiz --- USD \$1,500 (2025).}
  \resumeSubItem{Marshall Weinberg Population, Development and Climate Change Fellowship, Institute for Social Research, University of Michigan, \textit{Sustaining Public Infrastructure in Peru}. Lead-PI with Marcia Ruiz --- USD \$8,500 (2025).}

  \resumeSubItem{International Growth Centre (IGC) Grant, \textit{Sustaining Shared Urban Sanitation in Uganda}. Lead-PI with Marcia Ruiz and Laston Manja --- USD \$28,500 (2025).}

  \resumeSubItem{The Weiss Fund, \textit{Ghana Malaria Vaccine Adherence RCT}. Co-Investigator, with Jessica Cohen and Elisa Maffioli. USD \$199,000 (2025).}
  \resumeSubItem{Global Development Incubator, \textit{Ghana Malaria Vaccine Adherence RCT}. Co-Investigator, with Jessica Cohen and Elisa Maffioli. USD \$1,220,000 (2025).}

  \resumeSubItem{Economic and Social Research Consortium (CIES/USAID), \textit{Peruvian Public Health System: A Machine Learning Approach}. With Pedro Francke --- USD \$5,000 (2020).}
  \resumeSubItem{National Institute of Statistics and Information (INEI), \textit{The Effects of Social Programs on Malnutrition} --- USD \$7,000 (2019).}
  \resumeSubItem{Superintendence of Banks, Insurance and PFAs, Scholarship for Advanced Economics Program (2018).}
  \resumeSubItem{PUCP Economics Department, First Place in Research Paper Thesis Competition (2018).}
  \resumeSubItem{International Student Exchange Program Scholarship, Australian National University --- AUD \$5,000 (2017).}
\resumeSubHeadingListEnd

%-----------PRESENTATIONS-----------
\section{Seminars and Conferences}
\resumeSubHeadingListStart
  \resumeSubItem{RIDGE Summer School, Barbados. May 2026.}
  \resumeSubItem{Arnold Ventures BRIDGE Event on Online Harassment and Stalking, Washington, DC. April 2026.}
  \resumeSubItem{Midwest Economics Association Conference, Chicago, IL (participant). March 2026.}
  \resumeSubItem{University of Ghana School of Public Health Seminar, Accra, Ghana. ``Imprecise Beliefs About Malaria Infection Risk and Vaccine Protection in Ghana.'' October 2025.}
  \resumeSubItem{Empirical Study of Gender (EGEN) Pakistan Workshop II, CERP, Lahore, Pakistan. ``Impact of the COVID-19 Pandemic on Labor Markets in Pakistan.'' March 2022.}
  \resumeSubItem{DevLab Seminar, Duke University, Durham, NC. ``Impact of the COVID-19 Pandemic on Labor Markets in Pakistan.'' November 2021.}
  \resumeSubItem{CIES Annual Research Seminar, Lima, Peru. With Pedro Francke and Diego Quispe. ``At the Other Extreme: Does the Qali Warma Program Increase the Incidence of Overweight and Obesity Among Boys and Girls Ages 3 to 5?'' November 2020.}
  \resumeSubItem{\href{https://www.poverty-action.org/event/ipa-peru-presents-results-gender-based-violence-study}{Presentation of Pilot Results from a Group-Based Intervention to Peru's Minister of Women}, Lima, Peru. February 2020.}
\resumeSubHeadingListEnd

%-----------CURRENT COLLABORATIONS-----------
\section{Current Collaborations}
\resumeSubHeadingListStart
  \resumeSubItem{Ministry of Women and Vulnerable Populations, Peru, 2018--Present}
  \resumeSubItem{Ministry of Housing, Construction, and Sanitation, Peru, 2024--Present}
  \resumeSubItem{Ghana Health Services, Ghana, 2025--Present}
  \resumeSubItem{Ministry of Lands, Housing and Urban Development, Uganda, 2025--Present}
  \resumeSubItem{Ministry of Health, Uganda, 2026--Present}
  \resumeSubItem{Kampala Capital City Authority, Uganda, 2025--Present}
  \resumeSubItem{Banca de las Oportunidades, Colombia, 2026--Present}
\resumeSubHeadingListEnd

%-----------TEACHING EXPERIENCE-----------
\section{Teaching Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Michigan}{}{Teaching Assistant, Economics 101}{2024--2026}
  \resumeSubheading
    {Pontifical Catholic University of Peru}{}{Adjunct Professor, Thesis Seminar I}{2026}
  \resumeSubheading
    {Pontifical Catholic University of Peru}{}{Teaching Assistant, Macroeconomics}{2018}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{\textbf{Software}: Stata, R, Julia, Python, Matlab, SurveyCTO, Qualtrics, \LaTeX}
  \resumeSubItem{\textbf{Languages}: Spanish (native), English (professional proficiency), Chinese (basic proficiency)}
\resumeSubHeadingListEnd

\end{document}
